---
title: "Project Figures"
author: "Chloe Browne"
date: "2024-07-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## LOAD PACKAGES
```{r}
library(ggplot2)

library(dplyr)

library(tidyr)

library(scales)

# install.packages("patchwork")
library(patchwork)

# install.packages("devtools")
library(tidyverse)

# install.packages("tidyselect")
library(tidyselect)
```

## LOAD DATA
```{r}
prop3 <- readRDS(file = "prop3.rds")
```

## ORGANIZE VARIABLES

Duplicate Dependent Variables to Make them Independent
```{r}
# Prop 3
prop3 <- prop3 %>%
  mutate(ballot_combine_IV = ballot_combine)

# Legality
prop3 <- prop3 %>%
  mutate(vote5b_IV = vote5b)

# Identity
prop3 <- prop3 %>%
  mutate(vote5c_IV = vote5c)
```

Dependent Variables
```{r}
dvs = c("ballot_combine", "vote5b", "vote5c")

# Prop 3
bc = prop3[!is.na(prop3$ballot_combine),]

# Legality
v5b = prop3[grepl("egal", prop3$vote5b),]

# Identity
v5c = prop3[grepl("Pro-", prop3$vote5c),]
```

Independent Variables
```{r}
ivs = c("CD1",
        "generation",
        "edu_words",
        "race_combine",
        "religion_combine",
        "partyid",
        "ideology",
        "ballot_combine_IV",
        "vote5b_IV",
        "vote5c_IV")

iv_clean = c("Sex", 
             "Generation",
             "Education", 
             "Race",
             "Religion", 
             "Party ID",
             "Ideology",
             "Proposal Position", 
             "Legality Opinion", 
             "Self-Identification")
```

## ORGANIZE DEPENDENT VARIABLES

Proposal 3
```{r}
# Function Inputs
ggdata1 = bc
dv = "ballot_combine"
ivs = ivs

# Subset Relevant Variables
ggdata1 = ggdata1 %>% 
  select(all_of(c(ivs, dv)))

# Relabel Columns
names(ggdata1)[-ncol(ggdata1)] = iv_clean

# Organize for DV Column and IV Elongated
ggdata1 = ggdata1 %>% 
  pivot_longer(cols = all_of(iv_clean),
               names_to = "iv",
               values_to = "iv_value")

# Drop NAs
ggdata1 = na.omit(ggdata1)

# Drop "Skipped", "Not Asked", "I don’t know"
ggdata1 = ggdata1 %>%
  filter(!iv_value %in% c("skipped", 
                          "not asked", 
                          "I don’t know"))

# Summary Stats
ggdata1 =  ggdata1 %>% 
  group_by(!!sym(dv), iv, iv_value) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  group_by(iv, iv_value) %>%
  mutate(denom = sum(n)) %>%
  ungroup() %>%
  mutate(percent = n/denom)

# Create Text Column
ggdata1 = ggdata1 %>%
  mutate(perc_label = paste0(round(percent*100, 1), "%"))

# Create Percent Column, Make Opposing = Negative
ggdata1 = ggdata1 %>%
  mutate(plot_percent = ifelse(!!sym(dv) == "Oppose", -percent, percent))
```

Legality
```{r}
# Function Inputs
ggdata2 = v5b
dv = "vote5b"
ivs = ivs

# Subset Relevant Variables
ggdata2 = ggdata2 %>% 
  select(all_of(c(ivs, dv)))

# Relabel Columns
names(ggdata2)[-ncol(ggdata2)] = iv_clean

# Organize for DV Column and IV Elongated
ggdata2 = ggdata2 %>% 
  pivot_longer(cols = all_of(iv_clean),
               names_to = "iv",
               values_to = "iv_value")

# Drop NAs
ggdata2 = na.omit(ggdata2)

# Drop "Skipped", "Not Asked", "I don’t know"
ggdata2 = ggdata2 %>%
  filter(!iv_value %in% c("skipped", 
                          "not asked", 
                          "I don’t know"))

# Summary Stats
ggdata2 =  ggdata2 %>% 
  group_by(!!sym(dv), iv, iv_value) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  group_by(iv, iv_value) %>%
  mutate(denom = sum(n)) %>%
  ungroup() %>%
  mutate(percent = n/denom)

# Create Text Column
ggdata2 = ggdata2 %>%
  mutate(perc_label = paste0(round(percent*100, 1), "%"))

# Create Percent Column, Make Illeegal = Negative
ggdata2 = ggdata2 %>%
  mutate(plot_percent = ifelse(!!sym(dv) == "Illegal in all circumstances", -percent, percent))
```

Identity
```{r}
# Function Inputs
ggdata3 = v5c
dv = "vote5c"
ivs = ivs

# Subset Relevant Variables
ggdata3 = ggdata3 %>% 
  select(all_of(c(ivs, dv)))

# Relabel Columns
names(ggdata3)[-ncol(ggdata3)] = iv_clean

# Organize for DV Column and IV Elongated
ggdata3 = ggdata3 %>% 
  pivot_longer(cols = all_of(iv_clean),
               names_to = "iv",
               values_to = "iv_value")

# Drop NAs
ggdata3 = na.omit(ggdata3)

# Drop "Skipped", "Not Asked", "I don’t know"
ggdata3 = ggdata3 %>%
  filter(!iv_value %in% c("skipped", 
                          "not asked", 
                          "I don’t know"))

# Summary Stats
ggdata3 =  ggdata3 %>% 
  group_by(!!sym(dv), iv, iv_value) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  group_by(iv, iv_value) %>%
  mutate(denom = sum(n)) %>%
  ungroup() %>%
  mutate(percent = n/denom)

# Create Text Column
ggdata3 = ggdata3 %>%
  mutate(perc_label = paste0(round(percent*100, 1), "%"))

# Create Percent Column, Make Pro-life = Negative
ggdata3 = ggdata3 %>%
  mutate(plot_percent = ifelse(!!sym(dv) == "Pro-life", -percent, percent))
```

## INDIVIDUAL DATASETS

Prop 3 + Legality
```{r}
gg1_legality = ggdata1 %>% 
  filter(iv == "Legality Opinion") %>%
  filter(iv_value != "Don't know")

gg1_legality$iv_value = factor(gg1_legality$iv_value,
                           levels=c("Legal under any circumstances",
                                    "Legal only under certain circumstances",
                                    "Illegal in all circumstances"))

gg1_legality
```
```{r}
write.csv(gg1_legality, file = "gg1_legality.csv", row.names = FALSE)
```

Prop 3 + Identity
```{r}
gg1_identity = ggdata1 %>% 
  filter(iv == "Self-Identification") %>%
  filter(iv_value != "Don't know")

gg1_identity$iv_value = factor(gg1_identity$iv_value,
                           levels=c("Pro-choice",
                                    "Pro-life"))

gg1_identity
```
```{r}
write.csv(gg1_identity, file = "gg1_identity.csv", row.names = FALSE)
```

Legality + Proposal 3
```{r}
gg2_proposal = ggdata2 %>% 
  filter(iv == "Proposal Position") %>%
  filter(iv_value != "Don't know")

gg2_proposal$iv_value = factor(gg2_proposal$iv_value,
                           levels=c("Support",
                                    "Oppose"))

gg2_proposal
```
```{r}
write.csv(gg2_proposal, file = "gg2_proposal.csv", row.names = FALSE)
```

Legality + Identity
```{r}
gg2_identity = ggdata2 %>% 
  filter(iv == "Self-Identification") %>%
  filter(iv_value != "Don't know")

gg2_identity$iv_value = factor(gg2_identity$iv_value,
                           levels=c("Pro-choice",
                                    "Pro-life"))

gg2_identity
```
```{r}
write.csv(gg2_identity, file = "gg2_identity.csv", row.names = FALSE)
```

Identity + Proposal 3
```{r}
gg3_proposal = ggdata3 %>% 
  filter(iv == "Proposal Position") %>%
  filter(iv_value != "Don't know")

gg3_proposal$iv_value = factor(gg3_proposal$iv_value,
                           levels=c("Support",
                                    "Oppose"))

gg3_proposal
```
```{r}
write.csv(gg3_proposal, file = "gg3_proposal.csv", row.names = FALSE)
```

Identity + Legality
```{r}
gg3_legality = ggdata3 %>% 
  filter(iv == "Legality Opinion") %>%
  filter(iv_value != "Don't know")

gg3_legality$iv_value = factor(gg3_legality$iv_value,
                           levels=c("Legal under any circumstances",
                                    "Legal only under certain circumstances",
                                    "Illegal in all circumstances"))

gg3_legality
```
```{r}
write.csv(gg3_legality, file = "gg3_legality.csv", row.names = FALSE)
```

Prop 3 + Sex
```{r}
gg1_Sex = ggdata1 %>% 
  filter(iv == "Sex") %>%
  filter(iv_value != "Don't know")

gg1_Sex$iv_value = factor(gg1_Sex$iv_value,
                           levels=c("Male",
                                    "Female"))

gg1_Sex
```
```{r}
write.csv(gg1_Sex, file = "gg1_Sex.csv", row.names = FALSE)
```

Legality + Sex
```{r}
gg2_Sex = ggdata2 %>% 
  filter(iv == "Sex") %>%
  filter(iv_value != "Don't know")

gg2_Sex$iv_value = factor(gg2_Sex$iv_value,
                           levels=c("Male",
                                    "Female"))

gg2_Sex
```
```{r}
write.csv(gg2_Sex, file = "gg2_Sex.csv", row.names = FALSE)
```

Identity + Sex
```{r}
gg3_Sex = ggdata3 %>% 
  filter(iv == "Sex") %>%
  filter(iv_value != "Don't know")

gg3_Sex$iv_value = factor(gg3_Sex$iv_value,
                           levels=c("Male",
                                    "Female"))

gg3_Sex
```
```{r}
write.csv(gg3_Sex, file = "gg3_Sex.csv", row.names = FALSE)
```

Prop 3 + Generation
```{r}
gg1_Generation = ggdata1 %>% 
  filter(iv == "Generation") %>%
  filter(iv_value != "Don't know")

gg1_Generation$iv_value = factor(gg1_Generation$iv_value,
                           levels=c("Gen Z",
                                    "Millennial",
                                    "Gen X",
                                    "Baby Boomer",
                                    "Silent Generation"))

gg1_Generation
```
```{r}
write.csv(gg1_Generation, file = "gg1_Generation.csv", row.names = FALSE)
```

Legality + Generation
```{r}
gg2_Generation = ggdata2 %>% 
  filter(iv == "Generation") %>%
  filter(iv_value != "Don't know")

gg2_Generation$iv_value = factor(gg2_Generation$iv_value,
                           levels=c("Gen Z",
                                    "Millennial",
                                    "Gen X",
                                    "Baby Boomer",
                                    "Silent Generation"))

gg2_Generation
```
```{r}
write.csv(gg2_Generation, file = "gg2_Generation.csv", row.names = FALSE)
```

Identity + Generation
```{r}
gg3_Generation = ggdata3 %>% 
  filter(iv == "Generation") %>%
  filter(iv_value != "Don't know")

gg3_Generation$iv_value = factor(gg3_Generation$iv_value,
                           levels=c("Gen Z",
                                    "Millennial",
                                    "Gen X",
                                    "Baby Boomer",
                                    "Silent Generation"))

gg3_Generation
```
```{r}
write.csv(gg3_Generation, file = "gg3_Generation.csv", row.names = FALSE)
```

Prop 3 + Education
```{r}
gg1_Education = ggdata1 %>% 
  filter(iv == "Education") %>%
  filter(iv_value != "Don't know")

gg1_Education$iv_value = factor(gg1_Education$iv_value,
                           levels=c("Graduate degree",
                                    "Some post graduate", 
                                    "College degree", 
                                    "3rd year college", 
                                    "Technical/junior college graduate", 
                                    "2nd year college", 
                                    "1st year college", 
                                    "Diploma/GED",
                                    "No diploma/GED"))

gg1_Education
```
```{r}
write.csv(gg1_Education, file = "gg1_Education.csv", row.names = FALSE)
```

Legality + Education
```{r}
gg2_Education = ggdata2 %>% 
  filter(iv == "Education") %>%
  filter(iv_value != "Don't know")

gg2_Education$iv_value = factor(gg2_Education$iv_value,
                           levels=c("Graduate degree",
                                    "Some post graduate", 
                                    "College degree", 
                                    "3rd year college", 
                                    "Technical/junior college graduate", 
                                    "2nd year college", 
                                    "1st year college", 
                                    "Diploma/GED",
                                    "No diploma/GED"))

gg2_Education
```
```{r}
write.csv(gg2_Education, file = "gg2_Education.csv", row.names = FALSE)
```

Identity + Education
```{r}
gg3_Education = ggdata3 %>% 
  filter(iv == "Education") %>%
  filter(iv_value != "Don't know")

gg3_Education$iv_value = factor(gg3_Education$iv_value,
                           levels=c("Graduate degree",
                                    "Some post graduate", 
                                    "College degree", 
                                    "3rd year college", 
                                    "Technical/junior college graduate", 
                                    "2nd year college", 
                                    "1st year college", 
                                    "Diploma/GED",
                                    "No diploma/GED"))

gg3_Education
```
```{r}
write.csv(gg3_Education, file = "gg3_Education.csv", row.names = FALSE)
```

Prop 3 + Race
```{r}
gg1_Race = ggdata1 %>% 
  filter(iv == "Race") %>%
  filter(iv_value != "Don't know")

gg1_Race$iv_value = factor(gg1_Race$iv_value,
                           levels=c("African American",
                                    "Hispanic",
                                    "White",
                                    "Other Race"))

gg1_Race
```
```{r}
write.csv(gg1_Race, file = "gg1_Race.csv", row.names = FALSE)
```

Legality + Race
```{r}
gg2_Race = ggdata2 %>% 
  filter(iv == "Race") %>%
  filter(iv_value != "Don't know")

gg2_Race$iv_value = factor(gg2_Race$iv_value,
                           levels=c("African American",
                                    "Hispanic",
                                    "White",
                                    "Other Race"))

gg2_Race
```
```{r}
write.csv(gg2_Race, file = "gg2_Race.csv", row.names = FALSE)
```

Identity + Race
```{r}
gg3_Race = ggdata3 %>% 
  filter(iv == "Race") %>%
  filter(iv_value != "Don't know")

gg3_Race$iv_value = factor(gg3_Race$iv_value,
                           levels=c("African American",
                                    "Hispanic",
                                    "White",
                                    "Other Race"))

gg3_Race
```
```{r}
write.csv(gg3_Race, file = "gg3_Race.csv", row.names = FALSE)
```

Prop 3 + Religion
```{r}
gg1_Religion = ggdata1 %>% 
  filter(iv == "Religion") %>%
  filter(iv_value != "Don't know")

gg1_Religion$iv_value = factor(gg1_Religion$iv_value,
                           levels=c("None",
                                    "Other",
                                    "Catholic",
                                    "Protestant"))

gg1_Religion
```
```{r}
write.csv(gg1_Religion, file = "gg1_Religion.csv", row.names = FALSE)
```

Legality + Religion
```{r}
gg2_Religion = ggdata2 %>% 
  filter(iv == "Religion") %>%
  filter(iv_value != "Don't know")

gg2_Religion$iv_value = factor(gg2_Religion$iv_value,
                           levels=c("None",
                                    "Other",
                                    "Catholic",
                                    "Protestant"))

gg2_Religion
```
```{r}
write.csv(gg2_Religion, file = "gg2_Religion.csv", row.names = FALSE)
```

Identity + Religion
```{r}
gg3_Religion = ggdata3 %>% 
  filter(iv == "Religion") %>%
  filter(iv_value != "Don't know")

gg3_Religion$iv_value = factor(gg3_Religion$iv_value,
                           levels=c("None",
                                    "Other",
                                    "Catholic",
                                    "Protestant"))

gg3_Religion
```
```{r}
write.csv(gg3_Religion, file = "gg3_Religion.csv", row.names = FALSE)
```

Prop 3 + Party ID
```{r}
gg1_Party = ggdata1 %>% 
  filter(iv == "Party ID") %>%
  filter(iv_value != "Don't know")

gg1_Party$iv_value = factor(gg1_Party$iv_value,
                           levels=c("Strong Democrat", 
                                    "Lean Democrat", 
                                    "Not a very strong Democrat", 
                                    "Neither", 
                                    "Not a very strong Republican", 
                                    "Lean Republican",
                                    "Strong Republican"))

gg1_Party
```
```{r}
write.csv(gg1_Party, file = "gg1_Party.csv", row.names = FALSE)
```

Legality + Party ID
```{r}
gg2_Party = ggdata2 %>% 
  filter(iv == "Party ID") %>%
  filter(iv_value != "Don't know")

gg2_Party$iv_value = factor(gg2_Party$iv_value,
                           levels=c("Strong Democrat", 
                                    "Lean Democrat", 
                                    "Not a very strong Democrat", 
                                    "Neither", 
                                    "Not a very strong Republican", 
                                    "Lean Republican",
                                    "Strong Republican"))

gg2_Party
```
```{r}
write.csv(gg2_Party, file = "gg2_Party.csv", row.names = FALSE)
```

Identity + Party ID
```{r}
gg3_Party = ggdata3 %>% 
  filter(iv == "Party ID") %>%
  filter(iv_value != "Don't know")

gg3_Party$iv_value = factor(gg3_Party$iv_value,
                           levels=c("Strong Democrat", 
                                    "Lean Democrat", 
                                    "Not a very strong Democrat", 
                                    "Neither", 
                                    "Not a very strong Republican", 
                                    "Lean Republican",
                                    "Strong Republican"))

gg3_Party
```
```{r}
write.csv(gg3_Party, file = "gg3_Party.csv", row.names = FALSE)
```

Prop 3 + Ideology
```{r}
gg1_Ideology = ggdata1 %>% 
  filter(iv == "Ideology") %>%
  filter(iv_value != "Don't know")

gg1_Ideology$iv_value = factor(gg1_Ideology$iv_value,
                           levels=c("Very liberal", 
                                    "Somewhat liberal",
                                    "Closer to the liberal side",
                                    "In the middle", 
                                    "Closer to the conservative side",
                                    "Somewhat conservative", 
                                    "Very conservative"))

gg1_Ideology
```
```{r}
write.csv(gg1_Ideology, file = "gg1_Ideology.csv", row.names = FALSE)
```

Legality + Ideology
```{r}
gg2_Ideology = ggdata2 %>% 
  filter(iv == "Ideology") %>%
  filter(iv_value != "Don't know")

gg2_Ideology$iv_value = factor(gg2_Ideology$iv_value,
                           levels=c("Very liberal", 
                                    "Somewhat liberal",
                                    "Closer to the liberal side",
                                    "In the middle", 
                                    "Closer to the conservative side",
                                    "Somewhat conservative", 
                                    "Very conservative"))

gg2_Ideology
```
```{r}
write.csv(gg2_Ideology, file = "gg2_Ideology.csv", row.names = FALSE)
```

Identity + Ideology
```{r}
gg3_Ideology = ggdata3 %>% 
  filter(iv == "Ideology") %>%
  filter(iv_value != "Don't know")

gg3_Ideology$iv_value = factor(gg3_Ideology$iv_value,
                           levels=c("Very liberal", 
                                    "Somewhat liberal",
                                    "Closer to the liberal side",
                                    "In the middle", 
                                    "Closer to the conservative side",
                                    "Somewhat conservative", 
                                    "Very conservative"))

gg3_Ideology
```
```{r}
write.csv(gg3_Ideology, file = "gg3_Ideology.csv", row.names = FALSE)
```

## BARTENDER FUNCTION AND GRAPHS

Prop 3 Bartender Function = Creates Individual Graphs
```{r}
bartender1 = function(plot_data)
  {viz = ggplot(data = plot_data,
                aes(x = iv_value, 
                    y = plot_percent, 
                    fill = ballot_combine)) +
  geom_col(width = .9) +
  geom_text(aes(label = perc_label),
            position = position_stack(vjust = .5),
            color = "black",
            fontface = "bold",
            size = 5) +
  coord_flip() +    
  labs(x="", 
       y="",
       fill = "") +
  facet_wrap(~iv, 
             scales = "free_y") +
  theme_minimal() +
  theme(panel.grid = element_blank(),
        legend.position = "top",
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        text = element_text(color = "black", face = "bold", size = 20)) +
  scale_fill_manual(values = c("Oppose" = "indianred1",
                               "Support" = "limegreen")) +
  guides(fill = guide_legend(ncol = 1))
  #
  return(viz)}
```

Figure 1 Captions
```{r}
captions1 <- c("Figure 1.1",
              "Figure 1.2",
              "Figure 1.3",
              "Figure 1.4", 
              "Figure 1.5",
              "Figure 1.6",
              "Figure 1.7",
              "Figure 1.8",
              "Figure 1.9")
```

Prop 3 Graphs
```{r, fig.height = 30, fig.width = 10}
viz_gg1_legality = bartender1(gg1_legality)

viz_gg1_identity = bartender1(gg1_identity)

viz_gg1_Sex = bartender1(gg1_Sex)

viz_gg1_Generation = bartender1(gg1_Generation)

viz_gg1_Education = bartender1(gg1_Education)

viz_gg1_Race = bartender1(gg1_Race)

viz_gg1_Religion = bartender1(gg1_Religion)

viz_gg1_Party = bartender1(gg1_Party)

viz_gg1_Ideology = bartender1(gg1_Ideology)

##

prop3_all_dv_graph <- viz_gg1_legality + 
  viz_gg1_identity +
  viz_gg1_Sex + 
  viz_gg1_Generation + 
  viz_gg1_Education + 
  viz_gg1_Race + 
  viz_gg1_Religion + 
  viz_gg1_Party + 
  viz_gg1_Ideology + 
  plot_layout(ncol = 1, guides = "collect") +
  plot_annotation(title = "Do you oppose or support Proposal 3?\n", 
                  tag_levels = list(captions1),
                  theme = theme(plot.title = element_text(size = 20, face = "bold", hjust = 0.5))) &
  theme(legend.position = "top",
        plot.tag = element_text(size = 20, face = "bold"))

prop3_all_dv_graph
```

Save Bargraph
```{r}
ggsave(plot = last_plot(),
       filename = "prop3_all_dv_graph.png",
       height = 30, width = 10, units = "in", dpi = 600)
```

Legality Bartender Function = Creates Individual Graphs
```{r}
bartender2 = function(plot_data)
  {viz = ggplot(data = plot_data,
                aes(x = iv_value, 
                    y = plot_percent, 
                    fill = vote5b)) +
  geom_col(width = .9) +
  geom_text(aes(label = perc_label),
            position = position_stack(vjust = 0.5),
            color = "black",
            fontface = "bold",
            size = 5) +  
  coord_flip() +    
  labs(x="", 
       y="",
       fill = "") +
  facet_wrap(~iv, 
             scales = "free_y") +
  theme_minimal() +
  theme(panel.grid = element_blank(),
        legend.position = "top",
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        text = element_text(color = "black", face = "bold", size = 20)) +
  scale_fill_manual(values = c("Legal under any circumstances" = "royalblue", 
                               "Legal only under certain circumstances" = "mediumpurple", 
                               "Illegal in all circumstances" = "hotpink")) +
  guides(fill = guide_legend(ncol = 1))
  #
  return(viz)}
```

Figure 2 Captions
```{r}
captions2 <- c("Figure 2.1",
              "Figure 2.2",
              "Figure 2.3",
              "Figure 2.4", 
              "Figure 2.5",
              "Figure 2.6",
              "Figure 2.7",
              "Figure 2.8",
              "Figure 2.9")
```

Legality Graphs
```{r, fig.height = 30, fig.width = 10}
viz_gg2_proposal = bartender2(gg2_proposal)

viz_gg2_identity = bartender2(gg2_identity)

viz_gg2_Sex = bartender2(gg2_Sex)

viz_gg2_Generation = bartender2(gg2_Generation)

viz_gg2_Education = bartender2(gg2_Education)

viz_gg2_Race = bartender2(gg2_Race)

viz_gg2_Religion = bartender2(gg2_Religion)

viz_gg2_Party = bartender2(gg2_Party)

viz_gg2_Ideology = bartender2(gg2_Ideology)

##

legality_all_dv_graph <- viz_gg2_proposal + 
  viz_gg2_identity +
  viz_gg2_Sex + 
  viz_gg2_Generation + 
  viz_gg2_Education + 
  viz_gg2_Race + 
  viz_gg2_Religion + 
  viz_gg2_Party + 
  viz_gg2_Ideology + 
  plot_layout(ncol = 1, guides = "collect") + 
  plot_annotation(title = "Do you think abortions should be legal under any circumstances,\nlegal only under certain circumstances, or illegal in all circumstances?",
                  tag_levels = list(captions2),
                  theme = theme(plot.title = element_text(size = 20, face = "bold", hjust = 0.5))) &
  theme(legend.position = "top",
        plot.tag = element_text(size = 20, face = "bold"))

legality_all_dv_graph
```

Save Bargraph
```{r}
ggsave(plot = last_plot(),
       filename = "legality_all_dv_graph.png",
       height = 30, width = 10, units = "in", dpi = 600)
```

Identity Bartender Function = Creates Individual Graphs
```{r}
bartender3 = function(plot_data)
  {viz = ggplot(data = plot_data,
                aes(x = iv_value, 
                    y = plot_percent, 
                    fill = vote5c)) +
  geom_col(width = .9) +
  geom_text(aes(label = perc_label),
            position = position_stack(vjust = 0.5),
            color = "black",
            fontface = "bold",
            size = 5) +  
  coord_flip() +    
  labs(x="", 
       y="",
       fill = "") +
  facet_wrap(~iv, 
             scales = "free_y") +
  theme_minimal() +
  theme(panel.grid = element_blank(),
        legend.position = "top",
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        text = element_text(color = "black", face = "bold", size = 20)) +
  scale_fill_manual(values = c("Pro-choice" = "steelblue", 
                               "Pro-life" = "orange")) +
  guides(fill = guide_legend(ncol = 1))
  #
  return(viz)}
```

Figure 3 Captions
```{r}
captions3 <- c("Figure 3.1",
              "Figure 3.2",
              "Figure 3.3",
              "Figure 3.4", 
              "Figure 3.5",
              "Figure 3.6",
              "Figure 3.7",
              "Figure 3.8",
              "Figure 3.9")
```

Identity Graphs
```{r, fig.height = 30, fig.width = 10}
viz_gg3_proposal = bartender3(gg3_proposal)

viz_gg3_legality = bartender3(gg3_legality)

viz_gg3_Sex = bartender3(gg3_Sex)

viz_gg3_Generation = bartender3(gg3_Generation)

viz_gg3_Education = bartender3(gg3_Education)

viz_gg3_Race = bartender3(gg3_Race)

viz_gg3_Religion = bartender3(gg3_Religion)

viz_gg3_Party = bartender3(gg3_Party)

viz_gg3_Ideology = bartender3(gg3_Ideology)

##

identity_all_dv_graph <- viz_gg3_proposal + 
  viz_gg3_legality +
  viz_gg3_Sex + 
  viz_gg3_Generation + 
  viz_gg3_Education + 
  viz_gg3_Race + 
  viz_gg3_Religion + 
  viz_gg3_Party + 
  viz_gg3_Ideology + 
  plot_layout(ncol = 1, guides = "collect") +
  plot_annotation(title = "Would you consider yourself as pro-choice or pro-life?",
                  tag_levels = list(captions3),
                  theme = theme(plot.title = element_text(size = 20, face = "bold", hjust = 0.5))) &
  theme(legend.position = "top",
        plot.tag = element_text(size = 20, face = "bold"))

identity_all_dv_graph
```

Save Bargraph
```{r}
ggsave(plot = last_plot(),
       filename = "identity_all_dv_graph.png",
       height = 30, width = 10, units = "in",  dpi = 600)
```
