---
title: 'SOSS 85 Data'
author: "Lola Browne"
date: "2024-03-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### LOADING PACKAGES
```{r}
library(dplyr)
```

#### LOADING AND CREATING DATASET

# Load Survey Data
```{r}
survey <- read.csv("SSOS 85 Excel.csv")
```

# Survey Collumns
```{r}
colnames(survey)
```

# Make into New Data Set
```{r}
prop3 <- survey[c(1, 30:33, 76:99, 52:60)]
```

#### ASSIGNING DUMMBY VARIABLES

# vote5 = ballot
Are you likely to vote for or against the ballot initiative?
```{r}
# Vote for the ballot initiative
prop3$ballot[prop3$vote5 == "Support"] <- 1

# Vote against/Don’t change anything
prop3$ballot[prop3$vote5 == "Oppose"] <- 0

# I don’t know
prop3$ballot[prop3$vote5 == "I don‚Äôt know"] <- NA

#Skipped
prop3$ballot[prop3$vote5 == "skipped"] <- NA
```

# vote5a = ballot2
If you absolutely had to decide today, would you be likely to vote for or against a ballot initiative establishing reproductive rights, including abortion rights? (if vote5 ne <8> goto vote5a)
```{r}
# Vote for the ballot initiative
prop3$ballot2[prop3$vote5a == "Support"] <- 1

# Vote against/Don’t change anything
prop3$ballot2[prop3$vote5a == "Oppose"] <- 0

# I don’t know
prop3$ballot2[prop3$vote5a == "I don‚Äôt know"] <- NA

# Skipped
prop3$ballot2[prop3$vote5a == "skipped"] <- NA

# Not Asked
prop3$ballot2[prop3$vote5a == "not asked"] <- NA
```

# vote5b = legal1, legal2, legal3
Do you think abortions should be legal under any circumstances, legal only under certain circumstances, or illegal in all circumstances?
```{r}
# legal under any circumstances
prop3$legal1[prop3$vote5b == "Legal under any circumstances"] <- 1
prop3$legal1[prop3$vote5b == "Legal only under certain circumstances"] <- 0
prop3$legal1[prop3$vote5b == "Illegal in all circumstances"] <- 0

# legal only under certain circumstances
prop3$legal2[prop3$vote5b == "Legal only under certain circumstances"] <- 1
prop3$legal2[prop3$vote5b == "Legal under any circumstances"] <- 0
prop3$legal2[prop3$vote5b == "Illegal in all circumstances"] <- 0

# illegal in all circumstances
prop3$legal3[prop3$vote5b == "Illegal in all circumstances"] <- 1
prop3$legal3[prop3$vote5b == "Legal under any circumstances"] <- 0
prop3$legal3[prop3$vote5b == "Legal only under certain circumstances"] <- 0
```

# vote5c = abor_iden1 & abor_iden2
With respect to the abortion issue, would you consider yourself to be pro-choice or pro-life?
```{r}
# Pro-choice
prop3$abor_iden1[prop3$vote5c == "Pro-choice"] <- 1
prop3$abor_iden1[prop3$vote5c == "Pro-life"] <- 0

# Pro-life
prop3$abor_iden2[prop3$vote5c == "Pro-life"] <- 1
prop3$abor_iden2[prop3$vote5c == "Pro-choice"] <- 0

# I don’t know
prop3$abor_iden[prop3$vote5c == "I don‚Äôt know"] <- NA
```

# CD1 = sex
What is your sex?
```{r}
# Male
prop3$sex[prop3$CD1 == "Male"] <- 1

# Female
prop3$sex[prop3$CD1 == "Female"] <- 2
```

# CD2 = generation
In what year were you born?
```{r}
# Silent Generation
prop3$generation[prop3$CD2 >= 1928 & prop3$CD2 <= 1945] <- "Silent Generation"

# Baby Boomer
prop3$generation[prop3$CD2 >= 1946 & prop3$CD2 <= 1964] <- "Baby Boomer"

# Gen X
prop3$generation[prop3$CD2 >= 1965 & prop3$CD2 <= 1980] <- "Gen X"

# Millennial
prop3$generation[prop3$CD2 >= 1981 & prop3$CD2 <= 1996] <- "Millennial"

# Gen Z
prop3$generation[prop3$CD2 >= 1997 & prop3$CD2 <= 2012] <- "Gen Z"
```

# CD3 = edu
What is the highest level of education you have completed?
```{r}
# Did not go to school
prop3$edu[prop3$CD3 == "Did not go to school"] <- 0

# Did not graduate high school
prop3$edu[prop3$CD3 == "Did not graduate high school"] <- 1

# High school graduate or GED holder
prop3$edu[prop3$CD3 == "High school graduate or GED holder"] <- 2

# 1st year college
prop3$edu[prop3$CD3 == "1st year college"] <- 3

# 2nd year college
prop3$edu[prop3$CD3 == "2nd year college"] <- 4

# Technical/junior college graduate
prop3$edu[prop3$CD3 == "Technical/junior college graduate"] <- 5

# 3rd year college
prop3$edu[prop3$CD3 == "3rd year college"] <- 6

# College graduate (four years)
prop3$edu[prop3$CD3 == "College graduate (four years)"] <- 7

# Some post graduate
prop3$edu[prop3$CD3 == "Some post graduate"] <- 8

# Graduate degree
prop3$edu[prop3$CD3 == "Graduate degree"] <- 9
```

# CD3 = edu_words
What is the highest level of education you have completed?
```{r}
# No diploma/GED
prop3$edu_words[prop3$CD3 == "Did not go to school"] <- "No diploma/GED"
prop3$edu_words[prop3$CD3 == "Did not graduate high school"] <- "No diploma/GED"

# Diploma/GED
prop3$edu_words[prop3$CD3 == "High school graduate or GED holder"] <- "Diploma/GED"

# 1st year college
prop3$edu_words[prop3$CD3 == "1st year college"] <- "1st year college"

# 2nd year college
prop3$edu_words[prop3$CD3 == "2nd year college"] <- "2nd year college"

# Technical/junior college graduate
prop3$edu_words[prop3$CD3 == "Technical/junior college graduate"] <- "Technical/junior college graduate"

# 3rd year college
prop3$edu_words[prop3$CD3 == "3rd year college"] <- "3rd year college"

# College degree
prop3$edu_words[prop3$CD3 == "College graduate (four years)"] <- "College degree"

# Some post graduate
prop3$edu_words[prop3$CD3 == "Some post graduate"] <- "Some post graduate"

# Graduate degree
prop3$edu_words[prop3$CD3 == "Graduate degree"] <- "Graduate degree"
```

# CD5a = hispan
Are you of Hispanic, Latinx, or Spanish origin?
```{r}
# No, not of Hispanic/Latinx/Spanish origin
prop3$hispan[prop3$CD5a == "No, not of Hispanic/Latinx/Spanish origin"] <- 0

# Yes, Hispanic/Latinx/Spanish origin
prop3$hispan[prop3$CD5a == "Yes, Hispanic/Latinx/Spanish origin"] <- 1
```

# CD4_1 = white
What is your race (White or Caucasian)?
```{r}
# No, not White
prop3$white[prop3$CD4_1 == "not selected"] <- 0

# Yes, White
prop3$white[prop3$CD4_1 == "selected"] <- 1
```

# CD4_2 = afr_amer
What is your race (African American or Black)?
```{r}
# No, not African American or Black
prop3$afr_amer[prop3$CD4_2 == "not selected"] <- 0

# Yes, African American or Black
prop3$afr_amer[prop3$CD4_2 == "selected"] <- 1
```

# CD4_3 = pac_isla
What is your race (Hawaiian or other Pacific Islander)?
```{r}
# No, not Hawaiian or other Pacific Islander
prop3$pac_isla[prop3$CD4_3 == "not selected"] <- 0

# Yes, Hawaiian or other Pacific Islander
prop3$pac_isla[prop3$CD4_3 == "selected"] <- 1
```

# CD4_4 = asian
What is your race (Asian)?
```{r}
# No, not Asian
prop3$asian[prop3$CD4_4 == "not selected"] <- 0

# Yes, Asian
prop3$asian[prop3$CD4_4 == "selected"] <- 1
```

# CD4_5 = native
What is your race (American Indian or Alaska Native)?
```{r}
# No, not American Indian or Alaska Native
prop3$native[prop3$CD4_5 == "not selected"] <- 0

# Yes, American Indian or Alaska Native
prop3$native[prop3$CD4_5 == "selected"] <- 1
```

# CD4_6 = race_oth
What is your race (Other)?
```{r}
# No, not Other
prop3$race_oth[prop3$CD4_6 == "not selected"] <- 0

# Yes, Other
prop3$race_oth[prop3$CD4_6 == "selected"] <- 1
```

# CD6 = religion
What is the religious group which you feel most closely represents your religious views?
```{r}
# None; no religious group (Atheist, Agnostic, etc.)
prop3$religion[prop3$CD6 == "None; no religious group (Atheist, Agnostic, etc.)"] <- 0

# Catholic; Roman Catholic, Orthodox
prop3$religion[prop3$CD6 == "Catholic; Roman Catholic, Orthodox"] <- 1

# Islamic/Muslim
prop3$religion[prop3$CD6 == "Islamic/Muslim"] <- 2

# Jewish
prop3$religion[prop3$CD6 == "Jewish"] <- 3

# Protestant (Baptist, Methodist, Lutheran, Episcopalian, etc.)
prop3$religion[prop3$CD6 == "Protestant (Baptist, Methodist, Lutheran, Episcopalian, etc.)"] <- 4

# Other
prop3$religion[prop3$CD6 == "Other"] <- 5

# skipped
prop3$religion[prop3$CD6 == "skipped"] <- NA
```

# CD6_t = religion2
What is the religious group which you feel most closely represents your religious views (specify)?
```{r}
# None; no religious group (Atheist, Agnostic, etc.)
prop3$religion2[prop3$CD6_t == "agnostic" | 
                       prop3$CD6_t == "Believe in God" |
                       prop3$CD6_t == "faith" |
                       prop3$CD6_t == "Gnostic" |
                       prop3$CD6_t == "I believe in God" |
                       prop3$CD6_t == "I do believe in God but really not to a certain religion" |
                       prop3$CD6_t == "in GOD" |
                       prop3$CD6_t == "Just believe in God not religions" |
                       prop3$CD6_t == "Just beloe8ive in God" |
                       prop3$CD6_t == "My own beliefs." |
                       prop3$CD6_t == "none" |
                       prop3$CD6_t == "Not Religious" |
                       prop3$CD6_t == "Nothing in particular"] <- 0

# Catholic; Roman Catholic, Orthodox
prop3$religion2[prop3$CD6_t == "Catholic"] <- 1

# Jewish
prop3$religion2[prop3$CD6_t == "Hebrew/Bible beliver" |
                       prop3$CD6_t == "Messianic Jew" |
                       prop3$CD6_t == "Yahshuan"] <- 2

# Protestant (Baptist, Methodist, Lutheran, Episcopalian, etc.)
prop3$religion2[prop3$CD6_t == "7th Day Adventist" |
                       prop3$CD6_t == "American Baptist" |
                       prop3$CD6_t == "baptist" |
                       prop3$CD6_t == "Baptist" |
                       prop3$CD6_t == "A follower of Jesus's teachings" |
                       prop3$CD6_t == "Apostolic" |
                       prop3$CD6_t == "Born again christiann" |
                       prop3$CD6_t == "Chrismatic" |
                       prop3$CD6_t == "Christain" |
                       prop3$CD6_t == "christian" |
                       prop3$CD6_t == "Christian" |
                       prop3$CD6_t == "Christian faith" |
                       prop3$CD6_t == "Christian no denomination" |
                       prop3$CD6_t == "Christian Non-Denomination" |
                       prop3$CD6_t == "Christian without denomination" |
                       prop3$CD6_t == "Christian, no church affiliation" |
                       prop3$CD6_t == "Christianity" |
                       prop3$CD6_t == "Church of Christ" |
                       prop3$CD6_t == "Church of Jesus Christ of Latter-Day Saints" |
                       prop3$CD6_t == "Jehovah witness" |
                       prop3$CD6_t == "Jehovah‚Äôs Witnesses" |
                       prop3$CD6_t == "lutheran" |
                       prop3$CD6_t == "Lutheran" |
                       prop3$CD6_t == "Mormon" |
                       prop3$CD6_t == "Non denominational" |
                       prop3$CD6_t == "Non denominational christian" |
                       prop3$CD6_t == "Non denominational Christian" |
                       prop3$CD6_t == "Non domation" |
                       prop3$CD6_t == "non domimiational" |
                       prop3$CD6_t == "Non-Denomination" |
                       prop3$CD6_t == "non-denominational" |
                       prop3$CD6_t == "Non-denominational" |
                       prop3$CD6_t == "Nondenominational" |
                       prop3$CD6_t == "Pentecost" |
                       prop3$CD6_t == "Pentecostal" |
                       prop3$CD6_t == "Presbyterian" |
                       prop3$CD6_t == "Quaker" |
                       prop3$CD6_t == "Reformed Christian" |
                       prop3$CD6_t == "unaffiliated Christian" |
                       prop3$CD6_t == "Unitarian" |
                       prop3$CD6_t == "Unitarian Universalist" |
                       prop3$CD6_t == "Unitarian Universalist and Wicca"] <- 3

# Other
prop3$religion2[prop3$CD6_t == "Buddhism" |
                       prop3$CD6_t == "buddhist"] <- 4
prop3$religion2[prop3$CD6_t == "Hindu"] <- 4
prop3$religion2[prop3$CD6_t == "new age" |
                       prop3$CD6_t == "Spiritual" |
                       prop3$CD6_t == "Spiritual not religious" |
                       prop3$CD6_t == "Spiritual, not religious." |
                       prop3$CD6_t == "Spiritualist. The major religions are all about control."] <- 4
prop3$religion2[prop3$CD6_t == "Pagan" |
                       prop3$CD6_t == "Pagan/wiccan" |
                       prop3$CD6_t == "pagen"|
                       prop3$CD6_t == "Wiccan"] <-4
prop3$religion2[prop3$CD6_t == "Setian" |
                       prop3$CD6_t == "The Satanic Temple"] <- 4
prop3$religion2[prop3$CD6_t == "Natural life"] <- 4
prop3$religion2[prop3$CD6_t == "Native American people"] <- 4
prop3$religion2[prop3$CD6_t == "I believe many fit my beliefs"] <- 4
prop3$religion2[prop3$CD6_t == "Jedi"] <- 4
prop3$religion2[prop3$CD6_t == "__NA__"] <- 4
prop3$religion2[prop3$CD6_t == "NYFB"] <- 4
prop3$religion2[prop3$CD6_t == "Perfect not to answer to avoid discrimination"] <- 4
prop3$religion2[prop3$CD6_t == " "] <- 4
```

# CD7 = party
Generally speaking, do you think of yourself as a Republican, a Democrat, an Independent or something else?
```{r}
# Republican
prop3$party[prop3$CD7 == "Republican"] <- 1

# Democrat
prop3$party[prop3$CD7 == "Democrat"] <- 2

# Independent
prop3$party[prop3$CD7 == "Independent"] <- 3

# Another party, third party, etc
prop3$party[prop3$CD7 == "Another party, third party, etc"] <- 4

# skipped
prop3$party[prop3$CD7 == "skipped"] <- NA
```

# partyid = lean
Would you call yourself a strong Republican or not a very strong Republican? Would you call yourself a strong Democrat or not a very strong Democrat? Do you generally think of yourself as closer to the Democratic Party or the Republican Party?
```{r}
# Neither
prop3$lean[prop3$partyid == "Neither"] <- 0

# Strong Republican
prop3$lean[prop3$partyid == "Strong Republican"] <- 1

# Lean Republican
prop3$lean[prop3$partyid == "Lean Republican"] <- 2 

# Not a very strong Republican
prop3$lean[prop3$partyid == "Not a very strong Republican"] <- 3

# Strong Democrat
prop3$lean[prop3$partyid == "Strong Democrat"] <- 4

# Lean Democrat
prop3$lean[prop3$partyid == "Lean Democrat"] <- 5

# Not a very strong Democrat
prop3$lean[prop3$partyid == "Not a very strong Democrat"] <- 6

# skipped
prop3$lean[prop3$partyid == "skipped"] <- NA

# not asked
prop3$lean[prop3$partyid == "not asked"] <- NA
```

# partyid
Would you call yourself a strong Republican or not a very strong Republican? Would you call yourself a strong Democrat or not a very strong Democrat? Do you generally think of yourself as closer to the Democratic Party or the Republican Party?
```{r}
# Neither
prop3$partyid[prop3$partyid == "skipped"] <- "Neither"
prop3$partyid[prop3$partyid == "not asked"] <- "Neither"
```

# ideology = ideo_spec
Generally speaking, do you think of yourself as a conservative, a moderate, or a liberal?
```{r}
# Very conservative
prop3$ideo_spec[prop3$ideology == "Very conservative"] <- 1

# Somewhat conservative
prop3$ideo_spec[prop3$ideology == "Somewhat conservative"] <- 2

# Closer to the conservative side
prop3$ideo_spec[prop3$ideology == "Closer to the conservative side"] <- 3

# In the middle
prop3$ideo_spec[prop3$ideology == "In the middle"] <- 4

# Closer to the liberal side
prop3$ideo_spec[prop3$ideology == "Closer to the liberal side"] <- 5

# Somewhat liberal
prop3$ideo_spec[prop3$ideology == "Somewhat liberal"] <- 6

# Very liberal
prop3$ideo_spec[prop3$ideology == "Very liberal"] <- 7

# Don't know
prop3$ideo_spec[prop3$ideology == "Don't know"] <- NA

# skipped
prop3$ideo_spec[prop3$ideology == "skipped"] <- NA
```

## COMBINE VARIABLES
# vote5 + vote5a = ballot_combine, ballot_combine1, ballot_combine2
```{r}
prop3$ballot_combine[prop3$vote5 == "Support"] <- "Support"
prop3$ballot_combine[prop3$vote5a == "Support"] <- "Support"
prop3$ballot_combine[prop3$vote5 == "Oppose"] <- "Oppose"
prop3$ballot_combine[prop3$vote5a == "Oppose"] <- "Oppose"

# Support

prop3$ballot_combine1[prop3$ballot_combine == "Support"] <- 1
prop3$ballot_combine1[prop3$ballot_combine == "Oppose"] <- 0

# Oppose

prop3$ballot_combine2[prop3$ballot_combine == "Oppose"] <- 1
prop3$ballot_combine2[prop3$ballot_combine == "Support"] <- 0
```

# CD5a + CD4_1 + CD4_2 + CD4_3 + CD4_4 + CD4_5 + CD4_6 = race_combine
```{r}
# White
prop3$race_combine[prop3$CD4_1 == "selected"] <- "White"

# African American
prop3$race_combine[prop3$CD4_2 == "selected"] <- "African American"

# Pacific Islander
prop3$race_combine[prop3$CD4_3 == "selected"] <- "Pacific Islander"

# Hispanic
prop3$race_combine[prop3$CD5a == "Yes, Hispanic/Latinx/Spanish origin"] <- "Hispanic"

# Other Race
prop3$race_combine[prop3$CD4_6 == "selected"] <- "Other Race"
prop3$race_combine[prop3$CD4_4 == "selected"] <- "Other Race"
prop3$race_combine[prop3$CD4_5 == "selected"] <- "Other Race"
```

# CD6 + religion2 = religion_combine
```{r}
# Other
prop3$religion_combine[prop3$religion2 == 4] <- "Other"
prop3$religion_combine[prop3$CD6 == "Islamic/Muslim"] <- "Other"
prop3$religion_combine[prop3$CD6 == "Jewish"] <- "Other"
prop3$religion_combine[prop3$religion2 == 2] <- "Other"
prop3$religion_combine[prop3$CD6_t == "__NA__"] <- "Other"

# None
prop3$religion_combine[prop3$CD6 == "None; no religious group (Atheist, Agnostic, etc.)"] <- "None"
prop3$religion_combine[prop3$religion2 == 0] <- "None"

# Catholic
prop3$religion_combine[prop3$CD6 == "Catholic; Roman Catholic, Orthodox"] <- "Catholic"
prop3$religion_combine[prop3$religion2 == 1] <- "Catholic"

# Protestant
prop3$religion_combine[prop3$CD6 == "Protestant (Baptist, Methodist, Lutheran, Episcopalian, etc.)"] <- "Protestant"
prop3$religion_combine[prop3$religion2 == 3] <- "Protestant"
```

#### VARIABLE TOTALS

# vote5
```{r}
# Are you likely to vote for or against the ballot initiative?
table(prop3$vote5)
```

# vote5a
```{r}
# If you absolutely had to decide today, would you be likely to vote for or against a ballot initiative establishing reproductive rights, including abortion rights? (if vote5 ne <8> goto vote5a)
table(prop3$vote5a)
```

# ballot_combine
```{r}
# vote5 + vote5a
table(prop3$ballot_combine)
```

# vote5b
```{r}
# Do you think abortions should be legal under any circumstances, legal only under certain circumstances, or illegal in all circumstances?
table(prop3$vote5b)
```

# vote5c
```{r}
# With respect to the abortion issue, would you consider yourself to be pro-choice or pro-life?
table(prop3$vote5c)
```

# CD1
```{r}
# What is your sex?
table(prop3$CD1)
```

# CD2
```{r}
# In what year were you born?
table(prop3$CD2)
```

# generation
```{r}
# CD2 generations
table(prop3$generation)
```

# CD3
```{r}
# What is the highest level of education you have completed?
table(prop3$CD3)
```

# CD5a
```{r}
# Are you of Hispanic, Latinx, or Spanish origin?
table(prop3$CD5a)
```

# CD4_1
```{r}
# What is your race (White or Caucasian)?
table(prop3$CD4_1)
```

# CD4_2
```{r}
# What is your race (African American or Black)?
table(prop3$CD4_2)
```

# CD4_3
```{r}
# What is your race (Hawaiian or other Pacific Islander)?
table(prop3$CD4_3)
```

# CD4_4
```{r}
# What is your race (Asian)?
table(prop3$CD4_4)
```

# CD4_5
```{r}
# What is your race (American Indian or Alaska Native)?
table(prop3$CD4_5)
```

# CD4_6
```{r}
# What is your race (Other)?
table(prop3$CD4_6)
```

# race_combine
```{r}
# All races
table(prop3$race_combine)
```

# CD6
```{r}
# What is the religious group which you feel most closely represents your religious views?
table(prop3$CD6)
```

# CD6_t
```{r}
# What is the religious group which you feel most closely represents your religious views (specify)?
table(prop3$CD6_t)
```

# religion_combine
```{r}
# What is the religious group which you feel most closely represents your religious views (specify)?
table(prop3$religion_combine)
```

# CD7
```{r}
# Generally speaking, do you think of yourself as a Republican, a Democrat, an Independent or something else?
table(prop3$CD7)
```

# partyid
```{r}
# Would you call yourself a strong Republican or not a very strong Republican? Would you call yourself a strong Democrat or not a very strong Democrat? Do you generally think of yourself as closer to the Democratic Party or the Republican Party?
table(prop3$partyid)
```

# ideology
```{r}
# Generally speaking, do you think of yourself as a conservative, a moderate, or a liberal?
table(prop3$ideology)
```

#### ARRANGING FINAL DATA SET

```{r}
colnames(prop3)
```

```{r}
prop3 <- prop3 %>%
  select(caseid,
         vote5, ballot,
         vote5a, ballot2,
         ballot_combine, ballot_combine1, ballot_combine2,
         vote5b, legal1, legal2, legal3,
         vote5c, abor_iden1, abor_iden2,
         CD1, sex,
         CD2, generation,
         CD3,edu, edu_words,
         CD5a, hispan,
         CD4_1, white,
         CD4_2, afr_amer,
         CD4_3, pac_isla,
         CD4_4, asian,
         CD4_5, native,
         CD4_6, race_oth,
         race_combine,
         CD6, religion,
         CD6_t, religion2,
         religion_combine,
         CD7, party,
         partyid, lean,
         ideology, ideo_spec) %>%
  arrange(caseid)

head(prop3)
```

#### Save Final Data
```{r}
saveRDS(prop3, file = "prop3.rds")
```